---
title: "HW_09"
author: "izd3"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("HomeworkObjects.RData")
```


Use only commands \& functions that are shown in the indicated chapter or prior chapters.

\newpage

## Problem #01 - Chapter 34 Exercise #01B  

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
library(ggplot2)
library(scales)
scalesGraph000+scale_x_discrete(name='Flavors',labels=c('chocolate',
                                                        'raspberry'
                                                        ,'strawberry',
                                                        'vanilla'))+
  scale_fill_manual(values=c('red','white','black'),breaks = c('c','n','s'),
                    labels=c('chips','nuts','sprinkles'),name='Toppings')+
  scale_y_continuous(name='Frequency',breaks = NULL)

```

\newpage

## Problem #02 - Chapter 34 Exercise #02B  

```{r  out.height = 300, fig.height = 4, fig.width = 6}
# Show your work here
scalesGraph001+scale_size_manual(name='Flavor',
                                 labels=c('chocolate','strawberry', 
                                          'raspberry','vanilla'),
                                 values = c(4,3,2,1))

```


\newpage

## Problem #03 - Chapter 34 Exercise #04A ( top left )  

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
scaled001.dat|>
  ggplot(mapping = aes(x=weight,y=top,color=flav))+geom_jitter(shape=10)+
  scale_color_manual(name='Flavor',breaks = c('c','s','r','v'),
                     labels=c('Chocolate','Strawberry','Raspberry','Vanilla'),
                     values = c('blue','red','black','white'))

```

\newpage

## Problem #04 - Chapter 35 Exercise #01D   

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
scalesGraph002+scale_color_gradient(name='Red to Blue',
                                    low = 'red',high = 'blue')
```


\newpage

## Problem #05 - Chapter 35 Exercise #03A (red - blue)  

```{r  out.height = 300, fig.height = 4, fig.width = 6}
# Show your work here
scaled002.tib|>
  ggplot(mapping = aes(x=var.1,y=var.5,color=var.3))+geom_violin(fill='grey')+
  geom_point()+
  scale_x_log10(name='Log 10 Variable 1',breaks=c(1,5,10,15))+
  scale_color_gradient(name='VAR 3',low = 'red',high = 'blue')
  

```


\newpage

## Problem #06 - Chapter 37 Exercise #03B  

```{r  out.height = 300, fig.height = 4, fig.width = 6}
# Show your work here
library(forcats)
fact<-factor(factorData005.fact,levels = c('four star','three star'
                                           ,'two star','one star','zero star'))
table(fact)

unclass(fact)

```

\newpage

## Problem #07 - Chapter 37 Exercise #04B   

```{r  out.height = 300, fig.height = 4, fig.width = 6}
# Show your work here
table(factorData005.fact)

factorData005.fact<-fct_recode(factorData005.fact,`no stars`="zero stars",
                               `one,two, or three stars`='one star',
                               `one,two, or three stars`='two stars',
                 `one,two, or three stars`='three stars')
table(factorData005.fact)

```


\newpage

## Problem #08 - Chapter 33 Exercise #05E  

```{r  out.height = 300, fig.height = 4, fig.width = 6}
# Show your work here
  test<-data.frame(factorData006.fact=fct_infreq(factorData006.fact),
                   factorData004.fact =factorData004.fact)
test$factorData004.fact=factor(test$factorData004.fact,levels = LETTERS[11:20])
test|>
  ggplot(mapping = aes(x=factorData006.fact,fill=factorData004.fact))+
  geom_bar()+
  scale_fill_manual(breaks = LETTERS[11:20],
                    labels=LETTERS[11:20],
                    values = c('red','white','red','white','red','white',
                               'red','white','red','white'),drop=FALSE)+
  scale_x_discrete(breaks=c('reference','gnat','pig'),labels=c('REFERENCE',
                                                               'GNAT',
                                                               'PIG'))
```