---
title: "HW_11"
author: "izd3"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("HomeworkObjects.RData")
```

\newpage

## Problem #01 - Chapter 40 Exercise #03B (Alternating with all the given strings will get minimal credit) 

```{r  out.height = 300, fig.height = 4, fig.width = 12}
# Show your work here
library(stringr)
starting_strings <- c("A", "Ad", "Add", "Aing", "Ading", "Adding")
filtered_sentences <- str_subset(sentences, str_c("^", paste(starting_strings, collapse = "|")))
length(filtered_sentences)
filtered_sentences


```

\newpage

## Problem #02 - Chapter 40 Exercise #10  

```{r  out.height = 300, fig.height = 4, fig.width = 6}
# Show your work here

filtered_sentences <- str_subset(sentences, "^The.*ed.*the .*ed$")
filtered_sentences
```


\newpage

## Problem #03 - Chapter 40 Exercise #11 

```{r  out.height = 400, fig.height = 6, fig.width = 12}
# Show your work here
pattern <- "(er|se).*([a-zA-Z])\\2.*\\1"

# Create a single vector containing all strings that satisfy the specified conditions
filtered_sentences <- str_subset(sentences, pattern)

# Display the resulting vector
 filtered_sentences

```

\newpage


## Problem #04 - Chapter 41 Exercise #5 (display all this information in a single tibble/dataframe)  

```{r  out.height = 400, fig.height = 4, fig.width = 12}
# Show your work here
library(openintro)
library(dplyr)
data("nycflights")

nycflights|>
  group_by(carrier,origin)|>
  summarise(
    avg_dep_delay = mean(dep_delay, na.rm = TRUE),
    avg_arr_delay = mean(arr_delay, na.rm = TRUE),
    min_dep_delay = min(dep_delay, na.rm = TRUE),
    max_dep_delay = max(dep_delay, na.rm = TRUE),
    min_arr_delay = min(arr_delay, na.rm = TRUE),
    max_arr_delay = max(arr_delay, na.rm = TRUE)
  )

```


\newpage

## Problem #05 - Chapter 41 Exercise #06  

```{r  out.height = 300, fig.height = 4, fig.width = 6}
# Show your work here
library(babynames)
library(ggplot2)
babynames|>
  group_by(
    sex,year
  )|>
  summarise(max_num=max(n))|>
  ggplot(aes(y=max_num,x=year,color=sex))+geom_smooth(aes(linetype=sex))+
  labs(
    x="year",
    y="maximum"
  )

```


\newpage

## Problem #06 - Chapter 42 Exercise #2ABC 

```{r  out.height = 300, fig.height = 4, fig.width = 6}
# Show your work here
ChickWeight.tib|>
  filter(weight>350 | Time<1)

Formaldehyde.tib|>
  filter(carb<=0.3 & optden>0.2)

Loblolly.tib|>
  filter(age>=4&age<=10&Seed==329)

```

\newpage

## Problem #07 - Chapter 42 Exercise #03BD   

```{r  out.height = 300, fig.height = 4, fig.width = 6}
# Show your work here
library(lubridate)
Dates006.tib$dateData<-ydm(Dates006.tib$dateData)
Dates006.tib|>
  filter(dateData<"1910-01-01")

Dates007.tib$date.data=make_date(year = Dates007.tib$years.data,
                                 month = match(Dates007.tib$months.data,month.abb),
                                 day = Dates007.tib$days.data)

Dates007.tib|>
  filter(date.data>= "1960-02-01" & date.data <= "1962-09-02")

```


\newpage

## Problem #08 - Chapter 42 Exercise #04C 

```{r  out.height = 300, fig.height = 4, fig.width = 6}
# Show your work here
answer<-ggplot002.tib|>
  arrange(desc(y))

answer<- rbind(head(answer, 10), tail(answer, 10))

answer

```