---
title: "HW_07"
author: "izd3"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("HomeworkObjects.RData")
```


Use only commands \& functions that are shown in the indicated chapter or prior chapters.

\newpage

## Problem #01 - Chapter 29 Exercise #01D  

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
library(scales)
library(ggplot2)
coordGraph002+coord_fixed(ratio=8/7)
```

\newpage

## Problem #02 - Chapter 29 Exercise #03D  

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here

coordGraph002+coord_trans(y=sqrt_trans(),x=reverse_trans())

```


\newpage

## Problem #03 - Chapter 30 Exercise #01D  

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
facetPlot004+facet_wrap(~ggplot005.dat$var.3)
```

\newpage

## Problem #04 - Chapter 30 Exercise #03D   

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
facetPlot006+facet_grid(ggplot006.dat$var.3~ggplot006.dat$var.4)

```


\newpage

## Problem #05 - Chapter 30 Exercise #04A  

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
ggplot005.dat|>
  ggplot(aes(x=var.1,y=var.2,color=var.3))+
  geom_point(shape=3,size=4)+
  facet_wrap(~ggplot005.dat$var.4)
```


\newpage

## Problem #06 - Chapter 31 Exercise #03A  

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
ggplot009.tib|>
  ggplot(aes(x=x.values,y=y.values))+geom_line()

```

\newpage

## Problem #07 - Chapter 31 Exercise #04D   

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
ggplot010.tib|>
  ggplot(aes(x=u.values,y=t.values,color=z.values))+geom_line()

```


\newpage

## Problem #08 - Chapter 31 Exercise #06  

```{r  out.height = 500, fig.height = 6, fig.width = 6}
# Show your work here
x<-c(-1,0,1,2,0,-2)
y<-c(0,0,0,1,1,1)
x_head<-c(0,0.29,0,-.29)
y_head<-c(4,4.5,5,4.5)
head_data<-data.frame(x.boat=x_head,y.boat=y_head)
boat_data<-data.frame(x.boat=x,y.boat=y)



x_values <- seq(-5, 2, length.out = 1000)  # 100

y_values<-c(sinpi(x_values)/2,sinpi(x_values)/2.7,sinpi(x_values)/6,sinpi(x_values)/3,
            sinpi(x_values)/7)

x_values<-rep.int(x_values,times = 5)
z_values<-rep(c('A','B','C','D','E'),each=1000)

 wavy<-data.frame(x.boat=x_values,y.boat=y_values,z.wave=z_values)




ggplot()+geom_polygon(data=boat_data,mapping = aes(x=x.boat,y=y.boat),
                      color='red',fill='red')+
    geom_line(mapping = aes(x=0,y=2:4))+
    geom_line(mapping = aes(x=c(0,1),y=c(2,1)))+
    geom_line(mapping = aes(x=c(0,-1),y=c(2,1)))+
    geom_line(mapping = aes(x=c(0,1.5),y=c(3.98,3)))+
    geom_line(mapping = aes(x=c(0,-1.5),y=c(3.98,3)))+
    geom_point(aes(x=0,y=4.28),size=20)+
    geom_line(data=wavy,mapping = aes(x=x.boat,y=y.boat,color=z.wave))+
    geom_hline(yintercept = 5,color='white')
```