---
title: "HW_01"
author: "izd3"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("HomeworkObjects.RData")
```


Use only commands \& functions that are shown in the indicated chapter or prior chapters.

\newpage

## Problem #01 - Chapter 04 Exercise #04

```{r}
# Show your work here
m_1=c(10,34,4,884,4)
m_2=c(11,21,39,73,34)
r=c(2,.5,19,98,23)
g<-12.6

g*((m_1*m_2)/r^2)
```



\newpage

## Problem #02 - Chapter 04 Exercise #05

```{r}
# Show your work here
nums<-c(0:19)

fork<-(1+sqrt(5))/2

Fib<-(fork^nums-(-fork)^-nums)/sqrt(5)
Fib

```

\newpage

## Problem #03 - Chapter 04 Exercise #06

```{r}
# Show your work here
hypo<-c(5,13,41,29,65)
other<-c(4,12,40,21,63)

adjacent<-sqrt(hypo^2-other^2)
adjacent

```

\newpage

## Problem #04 - Chapter 04 Exercise #07

```{r}
# Show your work here
ones<-c(1,1,1)
evens<-c(2,4,6, 8)
negatives<--c(10,20,30,120)
ninety_nine<-99

#a
c(ones,ones,ninety_nine)

#b
c(ones,evens,-negatives)

#c
c(ones,ninety_nine,-negatives,-negatives,ones,ones)

#d
c(ones-1,ones+4,ninety_nine-84,ones-1,ninety_nine-99)

```




\newpage

## Problem #05 - Chapter 05 Exercise #04

```{r}
# Show your work here
CharacterData003
strsplit(CharacterData003,split ="inches")
```

\newpage

## Problem #06 - Chapter 05 Exercise #05

```{r}
# Show your work here
paste('I like the letter',CharacterData004)

```

\newpage

## Problem #07 - Chapter 05 Exercise #06

```{r}
# Show your work here
first_take<-paste(CharacterData005,CharacterData006,sep = ' ',collapse = ' ')
first_take_num<-nchar(first_take)
substring(text = first_take,first = 0,last = first_take_num-3)

```

\newpage

## Problem #08 - Chapter 05 Exercise #07ad

```{r}
# Show your work here


chartr(old = 'abcdecfghijklmnopqrstuvwxyz', new =	c('defghfijklmnopqrstuvwxyzabc') ,CharacterData007)


chartr(old = 'abcdecfghijklmnopqrstuvwxyz', new =c('uvwxywzabcdefghijklmnopqrst'),CharacterData010)


```

\newpage

## Problem #09 - Chapter 05 Exercise #08

```{r}
# Show your work here
string_length <- nchar(CharacterData011)
substring(text = CharacterData011, first = 2, last = string_length - 4)

string_length <- nchar(CharacterData012)
substring(text = CharacterData012, first = 1, last = string_length - 3)


string_length <- nchar(CharacterData013)
substring(text = CharacterData013, first = 11, last = string_length)

```