---
title: "HW_05"
author: "izd3"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("HomeworkObjects.RData")
```


Use only commands \& functions that are shown in the indicated chapter or prior chapters.

\newpage

## Problem #01 - Chapter 22 Exercise #04  

```{r}
# Show your work here
my_vector<-c(1:3)
for (i in 4:40) {
  my_vector[i] <- sum(my_vector[(i - 3):(i - 1)])
}
my_vector

```

\newpage

## Problem #02 - Chapter 22 Exercise #05  

```{r}
# Show your work here
vector_22<- 1

for (i in 2:40) {
  vector_22[i] <- -2 * vector_22[i - 1]
}
vector_22

```


\newpage

## Problem #03 - Chapter 23 Exercise #07  

```{r}
# Show your work here
setdiff(Set001, Set002)

```

\newpage

## Problem #04 - Chapter 24 Exercise #9 ( The result should be a single vector with 21 values. The function you want to use is vectorized.)  

```{r}
# Show your work here
chooser<-Vectorize(choose)
ans<-chooser(20,0:20)
ans
```


\newpage

## Problem #05 - Chapter 24 Exercise #13   

```{r}
# Show your work here
min_values<-0
for (i in 1:1000) {
  values <- c(Math001[i], Math002[i], Math003[i], Math004[i])
  min_val <- min(values)
  min_values[i] <- min_val
}
min_values[1:20]

```


\newpage

## Problem #06 - Chapter 24 Exercise #14  

```{r}
# Show your work here
non_zero <- 0

# Loop through i from 1 to 1000
for (i in 1:1000) {
  values <- c(Math001[i], Math002[i], Math003[i], Math004[i])
  values <- values[!is.na(values)]
  min_val <- min(values)
  if (min_val >= 0) {
    non_zero <- non_zero + 1
  }
}
non_zero

```

\newpage

## Problem #07 - Chapter 24 Exercise #15   

```{r}
# Show your work here
MathOrdered <- Math005[order(Math005$comp2), ]

head(MathOrdered, 10)

```


\newpage

## Problem #08 - Chapter 25 Exercise #07  

```{r}
# Show your work here
p_values<-LETTERS[1:10]
sample(x=p_values,size = 3,replace = T)

```