---
title: "HW_08"
author: "izd3"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("HomeworkObjects.RData")
```


Use only commands \& functions that are shown in the indicated chapter or prior chapters.

\newpage

## Problem #01 - Chapter 32 Exercise #01D  

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
library(ggplot2)
oneVariable001.dat|>
  ggplot(mapping = aes(x=values))+geom_freqpoly(stat = 'bin',binwidth=0.5,color='red')

```

\newpage

## Problem #02 - Chapter 32 Exercise #02A  

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
oneVariable001.dat|>
  ggplot(mapping = aes(x=values,fill=animals))+geom_histogram(binwidth = 0.5,position = 'stack')

```


\newpage

## Problem #03 - Chapter 32 Exercise #03A  

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
oneVariable001.dat|>
  ggplot(mapping = aes(x=values,fill=animals))+
  geom_histogram(binwidth = 0.5,position = 'dodge')

```

\newpage

## Problem #04 - Chapter 32 Exercise #04B   

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
oneVariable001.dat|>
  ggplot(mapping = aes(x=animals,y=values,fill=animals))+geom_violin()+
  geom_boxplot(alpha=0.5)

```


\newpage

## Problem #05 - Chapter 32 Exercise #04C  

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
oneVariable001.dat|>
  ggplot(mapping = aes(x=drive,fill=animals))+
  geom_histogram(position = 'identity',alpha=0.5)+
  facet_wrap(~flops)

```


\newpage

## Problem #06 - Chapter 33 Exercise #01A  

```{r  out.height = 300, fig.height = 6, fig.width = 12}
# Show your work here
oneVariable001.dat|>
  ggplot(mapping = aes(x=values,y=drive))+geom_point()

```

\newpage

## Problem #07 - Chapter 33 Exercise #02AC ( Displayed Side-by-Side)   

```{r  out.height = 300, fig.height = 3, fig.width = 12}
# Show your work here
oneVariable002.dat|>
  ggplot(mapping = aes(x=values,y=drive))+geom_point()+
  geom_rug(aes(color=animals),sides = 'r')

oneVariable001.dat|>
  ggplot(mapping = aes(x=values,y=drive,color=flops))+geom_point()+
  geom_smooth(aes(linetype=animals),se=F,color='black')

```


\newpage

## Problem #08 - Chapter 33 Exercise #04  (Use Minard dataframes in HistData package)

```{r  out.height = 300, fig.height = 2, fig.width = 12}
# Show your work here
library(HistData)
Minard.cities|>
  ggplot(mapping = aes(x=lat,y=long))+geom_point()+
  geom_text(aes(label=city),nudge_y =-1 )+
  geom_ribbon(data = Minard.troops,
              mapping =aes(x=lat,y=long,
                        ymin=long-survivors/max(survivors),
                        ymax=long+survivors/max(survivors),fill=direction))
```