---
title: "HW_03"
author: "izd3"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("HomeworkObjects.RData")
```


Use only commands \& functions that are shown in the indicated chapter or prior chapters.

\newpage

## Problem #01 - Chapter 10 Exercise #02 

```{r}
# Show your work here

CharacterData001[10:15]
CharacterData006[(length(CharacterData006)-5):64]
Filtering001[1:20]

```

\newpage

## Problem #02 - Chapter 10 Exercise #04 

```{r}
# Show your work here
fill1<-which(Filtering001>=9.9)
Filtering001[fill1]

Filtering001[Filtering001>=0 & Filtering001<=0.025]

CharacterData001[CharacterData001=='if' | CharacterData001=='this']



```

\newpage

## Problem #03 - Chapter 11 Exercise #02 

```{r}
# Show your work here

fruitMatrix[,5]
```

\newpage

## Problem #04 - Chapter 11 Exercise #05 

```{r}
# Show your work here
str(fruitMatrix)
matrix(fruitMatrix[2:5,2:4],nrow = 4,ncol = 3,byrow = FALSE)

```

\newpage

## Problem #05 - Chapter 11 Exercise #08 

```{r}
# Show your work here
matrix(numberMatrix[numberMatrix<=25],nrow = 4,ncol = 4,byrow = FALSE)
```

\newpage

## Problem #06 - Chapter 12 Exercise #04 

```{r}
# Show your work here
library('stringr')
any(tolower(substr(sentences, length(sentences), length(sentences))) == 'z')

```

\newpage

## Problem #07 - Chapter 12 Exercise #05 

```{r}
# Show your work here
all(length(words)<=11)
```

\newpage

## Problem #08 - Chapter 13 Exercise #01 

```{r}
# Show your work here
length(PossiblyInfinite[PossiblyInfinite==Inf | PossiblyInfinite==-Inf])

```

\newpage

## Problem #09 - Chapter 14 Exercise #02ab 

```{r}
# Show your work here
anyNA(firstNames)
anyNA(lastNames)

```

\newpage

## Problem #10 - Chapter 14 Exercise #03 

```{r}
# Show your work here
which(is.na(MissingValues01))
which(is.na(MissingValues02))
which(is.na(MissingValues03))
which(is.na(firstNames))
which(is.na(lastNames))
which(is.na(idNumbers))
```

\newpage

## Problem #11 - Chapter 14 Exercise #05a 

```{r}
# Show your work here
casll<-which(is.na(lastNames))
firstNames[as.integer(casll)]
#Since there is no NA in last names nothing
#is shown for firstrNames
```



