---
title: "HW_04"
author: "izd3"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("HomeworkObjects.RData")
```


Use only commands \& functions that are shown in the indicated chapter or prior chapters.

\newpage

## Problem #01 - Chapter 16 Exercise #04  

```{r}
# Show your work here
string_a<-'a'
num_vec<-c(0,1)
xer<-rep(x=1,times=6)
mat_1 <- matrix(data = xer, nrow = 2, ncol = 3, byrow = FALSE)
na_vec<-rep(x=NA,times=10)
List004<-list(num_vec,xer,mat_1,as.character(na_vec))
str(List004)

```

\newpage

## Problem #02 - Chapter 17 Exercise #03 (Display the structure of your results and not the actual result.)  

```{r}
# Show your work here
str(ModifyLists001[1])
str(ModifyLists002[length(ModifyLists002)-1:length(ModifyLists002)])
len<-length(ModifyLists003)
vects<-seq(from=2,to=10,by=2)
str(ModifyLists003[vects])

```

\newpage

## Problem #03 - Chapter 17 Exercise #06 (Display the structure of your results and not the actual result.)  

```{r}
# Show your work here
copy<-ModifyLists003
copy<-(copy[names(copy)!=''])
str(copy)


```

\newpage

## Problem #04 - Chapter 18 Exercise #02 

```{r}
# Show your work here
letter3<-rep(x=letters,each=3)
nums<-seq(from=78,to=1)
cl<-colors()
ini<-length(cl)-77
cl<-cl[ini:length(cl)]

dat<-data.frame(variable.1=letter3,variable.2=nums,variable.3=cl)
dat

```

\newpage

## Problem #05 - Chapter 18 Exercise #06 (Display the structure of your results and not the actual result.)

```{r}
# Show your work here
str(subset(Loblolly,Loblolly$height>60))
str(subset(Formaldehyde,Formaldehyde$carb>0.5))
str(subset(ChickWeight,ChickWeight$weight==0))
```

\newpage

## Problem #06 - Chapter 19 Exercise #02 (Display the structure of your results and not the actual result.)

```{r}
# Show your work here
library('tibble')
letter3<-rep(x=letters,each=3)
nums<-seq(from=78,to=1)
cl<-colors()
ini<-length(cl)-77
cl<-cl[ini:length(cl)]

example.tibble2<-tibble(variable.1=letter3,variable.2=nums,variable.3=cl)
str(example.tibble2)

```


\newpage

## Problem #07 - Chapter 19 Exercise #05 

```{r}
# Show your work here
str(subset(Loblolly.tib,Loblolly$height>60))
str(subset(Formaldehyde.tib,Formaldehyde.tib$carb>0.5))
str(subset(ChickWeight.tib,ChickWeight.tib$weight==0))


```

\newpage

## Problem #08 - Chapter 20 Exercise #02 ( You will need to look up the formula) 

```{r}
# Show your work here
FtoC <- function(Fahrenheit) {
  Celsius <- (Fahrenheit - 32) * 5/9
  return(Celsius)
}

```

\newpage

## Problem #09 - Chapter 20 Exercise #08 ( You will need to look up the formula) 

```{r}
# Show your work here
ten0<-rep(x=0,times=10)

totalOfTen <- function(x = ten0) {
  total <- sum(x)
  return(total)
}

```

\newpage

## Problem #10 - Chapter 21 Exercise #07 ( You will need to look up the formulas) 

```{r}
# Show your work here
LifeCycleSavingsUpdate$age.ratio <- LifeCycleSavingsUpdate$pop15 / 
  LifeCycleSavingsUpdate$pop75

LifeCycleSavingsUpdate$broken.up <- ifelse(LifeCycleSavingsUpdate$age.ratio < 10
                                           
&LifeCycleSavingsUpdate$ddpi < 3,"DOWN"

,ifelse(LifeCycleSavingsUpdate$age.ratio > 20 & LifeCycleSavingsUpdate$ddpi > 4,
        "UP","OVER"))

head(LifeCycleSavingsUpdate)

```
