---
title: "HW_02"
author: "izd3"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("HomeworkObjects.RData")
```


Use only commands \& functions that are shown in the indicated chapter or prior chapters.

\newpage

## Problem #01 - Chapter 06 Exercise #01 ( Use the stringr package)

```{r}
# Show your work here
library('stringr')
str_c("Letter:",CharacterData004)


```



\newpage

## Problem #02 - Chapter 06 Exercise #04 ( Use the stringr package)

```{r}
# Show your work here
str_dup(string = "Ho!",times = c(9,8,7,6,5,4,3,2,1))

```

\newpage

## Problem #03 - Chapter 06 Exercise #05 ( Use the stringr package)

```{r}
# Show your work here
str_c("I like the letter",CharacterData004,".")
```

\newpage

## Problem #04 - Chapter 07 Exercise #04

```{r}
# Show your work here
c( T, T, F, F, TRUE ) & c(T,T,T,T,T)

!c(F, T, T,F,T,T) & c( F, T, F, T, T, F )

c( T, !FALSE, T, TRUE, T, T ) | c(F, F, !T,F,F,!T )

!c( FALSE, !FALSE, T, TRUE, T, T, FALSE ) | !c( !F, !F, !FALSE, T,!F,!F,!FALSE )

```




\newpage

## Problem #05 - Chapter 07 Exercise #05

```{r}
# Show your work here
any(c( T, T, F, F, TRUE ) & c(T,T,T,T,T))
all(c( T, T, F, F, TRUE ) & c(T,T,T,T,T))

any(!c(F, T, T,F,T,T) & c( F, T, F, T, T, F ))
all(!c(F, T, T,F,T,T) & c( F, T, F, T, T, F ))

any(c( T, !FALSE, T, TRUE, T, T ) | c(F, F, !T,F,F,!T ))
all(c( T, !FALSE, T, TRUE, T, T ) | c(F, F, !T,F,F,!T ))

any(!c( FALSE, !FALSE, T, TRUE, T, T, FALSE ) | !c( !F, !F, !FALSE, T,!F,!F,!FALSE ))
all(!c( FALSE, !FALSE, T, TRUE, T, T, FALSE ) | !c( !F, !F, !FALSE, T,!F,!F,!FALSE ))

```

\newpage

## Problem #06 - Chapter 08 Exercise #01

```{r}
# Show your work here
3==3L

c(1, 2, 3, 4, 5, 6)<4

set_one<-c(1:25)
set_two<-sqrt(set_one)^2
set_one >= set_two

set_three<-sqrt(set_one^2)
set_one<=set_three


```

\newpage

## Problem #07 - Chapter 09 Exercise #01

```{r}
# Show your work here
typeof(c(1, 2L, 3L, 4L, 5L, 6L, 7L, 8L))

typeof(c(T, T, T, T, "F"))

typeof(c(T, 1))

typeof(c('a', T, 10))

```

\newpage

## Problem #08 - Chapter 09 Exercise #03 (Do not display the 1000 element results.)

```{r}
# Show your work here

#a 
first<-seq(from=1,to=1000, by=1)
#b. 
second<-sqrt(first)
#c. 
third<-seq(from=2,to=1000,by=2)
third
#d. 
fourth<-seq(from=1,to=999,by=2)
fourth

#e. 
fifth<-seq(from=10,to=-50,by=-1)
fifth

```

\newpage

## Problem #09 - Chapter 09 Exercise #05

```{r}
# Show your work here
#a)
seq(from=-0.123, to=68, length.out=9)

#b)
seq(from=90,by=-12,length.out=19)

#c)
seq(from=9,by=3,to=21.2)

#d)
vec_1<-seq(from=10,to=2001,by=10)
sqrt(vec_1)

#e)
vec_2<-seq(from=82,to=2001,by=82)
sqrt(vec_2)+25

```


\newpage

## Problem #10 - Chapter 09 Exercise #06abc

```{r}
# Show your work here
#a)
c(VectorsOne,VectorsInts)

#b)
rep(c(VectorsA,VectorsGirl),length.out=100)


#c)
c(VectorsA,VectorsOne,VectorsA,VectorsGirl,VectorsInts,VectorsA)

```


\newpage

## Problem #11 - Chapter 09 Exercise #07a

```{r}
# Show your work here
seq(from=156, to=10000, by=pi)
```